\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{amsthm}


\setlength{\parindent}{24pt}

\begin{document}

\begin{enumerate}
    \item (a) is equivalent to (i) because they are their contrapositives, and
          equal to (g) and (f) since they are the same thing but reworded.
           (h) is the contrapositive of (b) so they are equal and
          they are also equal to (e). By definition, (c) and (d) are
          equivalent.

    \item If x, y are both even integers $(P)$, then the sum is even $(Q)$. The converse
          is if a number is even$(Q)$, then it must have been added by two even
          integers$(P)$, but $\frac{3}{2} + \frac{1}{2} = 2$, which is even, so the
          converse is false.

    \item The converse is equivalent logically to the inverse because they are their
    contrapositives, which are always logically equivalent.

    \item They are not equivalent. Let $P(x,y)$ equal $x < y$. Notice that the statement
          ``$\forall x \exists y$'' is always true since there is always a number less
          than another, but the statement ``$\forall y \exists x$'' says all numbers are
          less than $y$, which is false since there is no number less than all numbers.

    \item
          \begin{enumerate}
              \item Since we are given that $x$ is an integer, then we can seperate the cases where
                    $x$ is odd and even. \newline Case $x$ is odd:

                    \begin{quote}
                        By definition, we can represent $x$ as $2n + 1$ for some integer $n$.
                        Substituting that into $x^2+5x$, we get:
                        \begin{center}$x^2+5x = (2n+1)^2 + 5(2n+1)$ \end{center}
                        and after simplifying and combining like terms we get:
                        \begin{center}$4n^2 + 14n + 6$ \end{center}
                        Letting $m = 2n^2 + 7n + 3$, we have:
                        \begin{center}$2(2n^2+7n+3) = 2m$\end{center}
                        which is even.
                    \end{quote}
                    Case $x$ is even:
                    \begin{quote}
                        By definition, we can represent $x$ as $2n$ for some integer $n$.
                        Substituting into $x^2 + 5x$, we get
                        \begin{center}
                            $x^2+5x = (2n)^2 + 5(2n) = 4n^2 + 10n$
                        \end{center}
                        Letting $m = 2n^2 + 5n$, we have
                        \begin{center}
                            $2(2n^2+5n) = 2m$
                        \end{center}
                        which is also even.
                    \end{quote}
                    Therefore, for all integers, $x^2+5x$ is even. \hfill $\blacksquare$
              \item By definition, we can represent an odd integer as $2n+1$ for some integer $n$.
                    Substituting into $x^3-3x^2+5x+7$, we have
                    \begin{center}
                        $x^3-3x^2+5x+7 = (2n+1)^3-3(2n+1)^2+5(2n+1)+7$
                    \end{center}
                    and after expanding and collecting like terms, we get
                    \begin{center}
                        $8n^3 + 4n + 10$.
                    \end{center}
                    Letting $m = 4n^3 + 2n + 5$, we have
                    \begin{center}
                        $2(4n^3+2n+5) = 2m$,
                    \end{center}
                    which is even. Hence if x is odd, $x^3-3x^2+5x+7$ is even. \hfill $\blacksquare$
              \item Note that the a statement and its contrapositive are equivalent so proving that
                    the contrapositive is true will be sufficient. Since we are given that $x$ is
                    an integer, the contrapositive of the statement is if $x$ is even, then
                    $x^2+2x+3$ is odd. Letting $x = 2n$, we have
                    \begin{center}
                        $x^2+2x+3 = (2n)^2+2(2n) + 3 = 4n^2 + 4n + 3$.
                    \end{center}
                    Letting $m = 2n^2+2n+1$, we get
                    \begin{center}
                        $4n^2 + 4n + 3 = 2(2n^2+2n+1) + 1 = 2m + 1$,
                    \end{center}
                    which is odd. \hfill $\blacksquare$
              \item Since $x$ is an integer, we can seperate the cases into when it's odd and even.
                    \newline Case $x$ is even:
                    \begin{quote}
                        Let $x = 2m$ for some integer m (so $x$ is even by definition).
                        Substituting into $n^2$, we have
                        \begin{center}
                            $n^2 = (2m)^2 = 4m^2$.
                        \end{center}
                        Let $k = m^2$. Then
                        \begin{center}
                            $4m^2 = 4k$,
                        \end{center}
                        which is divisible by $4$.
                    \end{quote}
                    Case $x$ is odd:
                    \begin{quote}
                        Let $x = 2m + 1$ for some integer m (so $x$ is odd by definition).
                        Substituting into $n^2+1$, we get
                        \begin{center}
                            $n^2+1 = (2m+1)^2-1 = 4m^2 + 4m$
                        \end{center}
                        Let $k = m^2 + m$. Then
                        $4m^2 + 4m = 4(m^2+m) = 4k$,
                        Which is also divisible by 4.
                    \end{quote}
                    Therefore, for all integers, either $n^2$ or $n^2-1$ is a multiple
                    of $4$. \hfill $\blacksquare$
          \end{enumerate}
    \item Since this is 4 consecutive numbers, then there will be at least 2 even
          numbers, and one of them is a multiple of 4, and there will be one a factor of
          3. This gives at minimum factors 2, 3, and 4. This means the largest $n$ such
          that $x(x+1)(x+2)(x+3)$ is a multiple of n is $2 \times 3 \times 4 = 24$.
          \hfill $\blacksquare$
    \item First, assume that $\sqrt{3}$ is rational, so then it can be represented as a
          fraction of two integers, $a$ and $b$: $\frac{a}{b}$, where $b$ is positive and
          as small as possible. Now, square both sides to get
          \begin{center}
              $3 = \frac{a^2}{b^2}$,
          \end{center}
          and rearange to get
          \begin{center}
              $3b^2 = a^2$.
          \end{center}
          Now, notice that since the left side is a multiple of 3, then the right side
          must be a multiple of 3 as well, so we can let $a = 3c$ for some integer $c$.
          So now we have
          \begin{center}
              $3b^2 = (3c)^2 = 9c^2$,
          \end{center}
          and dividing both sides by 3 gives $b^2 = 3c^2$. Rearanging and taking the
          square root of both sides gives
          \begin{center}
              $\sqrt{3} = \frac{b}{c}$
          \end{center}
          with $b>c>0$. This is a contradiction since we have just written $\sqrt{3}$
          as a fraction with a denominator smaller than $b$. This means that our
          initial assumption that $\sqrt{3}$ is rational must be false. Thus, $\sqrt{3}$
          is irrational. \hfill $\blacksquare$\newline
          Proof for $\sqrt[3]{4}$:
          First, assume that $\sqrt[3]{4}$ is rational, so then it can be represented as a
          fraction of two integers, $a$ and $b$: $\frac{a}{b}$, where $b$ is positive and 
          as small as possible. Now, cube both sides to get $4 = \frac{a^3}{b^3}$, then 
          multiply both sides by $b^3$ to get $4b^3 = a^3$. Since the left side is even, 
          then the right side mut be as well, so we can let $a = 2c$ for some integer $c$:
          $4b^3 = (2c)^3 = 8c^3$. Dividing both sides by 4 gives $b^3 = 2c^3$. Again, since 
          the right side is even, the left must be as well, so we can let $b = 2d$ for some
          integer $d$: $2c^3 = (2d)^3 = 8d^3$. Dividing both sides by 2 now gives $c^3 = 4d^3$.
          After rearanging, we have 
          \begin{center}
            $\sqrt[3]{4} = \frac{c}{d}$,
          \end{center}
          Which contradicts our original assumption that $\sqrt[3]{4}$ was written with
          it's denominator as small as possible. Hence, $\sqrt[3]{4}$ is irrational. \hfill $\blacksquare$
          \newline
          When trying to do the same thing for $\sqrt9$, during the substitution step,
          you end up with something like $9b^2 = a^2$ and since 9 is a multiple of 3, 
          we can substitute $a = 3c$ for some integer $c$ and get $9b^2 = 9c^2$, and 
          dividing both sides by 9 gives $b^2 = c^2$, so no contradiction (obviously 
          since $\sqrt9 = 3$, which is rational).
          \item Let $j$ be an irrational number. First, we falsely assume that adding an 
          irrational number, $j$, with a rational number, $\frac{a}{b}$, will result 
          in a rational number, $\frac{c}{d}$, for some integers $a,b,c, $ and $d$ 
          where $b, d \neq 0$. Then 
          \begin{align*}
            j + \frac{a}{b} &= \frac{c}{d}\\
            j &= \frac{c}{d} - \frac{a}{b} 
          \end{align*}
            and finding a common denominator gives
          \begin{align*}
            j = \frac{cb-ad}{db}.
          \end{align*}
          Letting $p = cb-ad$ and $q = db$, we have
          \begin{align*}
            j = \frac{p}{q},
          \end{align*}
          Which is a contradiction to our assumption that $j$ is irrational, hence 
          adding an irrational number with a rational one is irrational. \hfill $\blacksquare$\newline\newline
          Next, consider irrational numbers $\sqrt2$ and $-\sqrt2$. Their sum is 
          \begin{align*}
            \sqrt2 + (-\sqrt2) = 0,
          \end{align*}
          which is rational, hence there are two rational numbers whose sum is 
          rational. \hfill $\blacksquare$ 
          \item First, we falsely assume that multiplying an 
          irrational number, $j$, with a rational number, $\frac{a}{b}$, will result 
          in a rational number, $\frac{c}{d}$, for some integers $a,b,c, $ and $d$ 
          where $a,b,d \neq 0$. Then 
          \begin{align*}
            j \times \frac{a}{b} &= \frac{c}{d}.
          \end{align*}
          Multiplying both sides by $b$ and dividing by $a$ gives
          \begin{align*}
            j &= \frac{bc}{ad}.
          \end{align*}
          Letting $p = bc$ and $q = ad$ gives $j = \frac{p}{q}$, which contradicts 
          our original assumption that j is irrational, hence, multiplying a rational 
          number with an irrational one is irrational. \hfill $\blacksquare$

          To prove there are two irrational whose product is rational we can multiply
          $\sqrt2$ with itself:
          \begin{align*}
            \sqrt2 \times \sqrt2 = 2,
          \end{align*}
          which is rational, so there exists two irrational numbers whose product
          is rational. \hfill $\blacksquare$
          \item First, we falsly assume that $x$ can be represented as a fraction
          of two integers, $a$ and $b$. Then 
          \begin{align*}
            2^\frac{a}{b} = 3,
          \end{align*}
          and raising both sides to the power of $b$ gives
          \begin{align*}
            (2^\frac{a}{b})^b &= (3)^b \\
            2^a &= 3^b
          \end{align*}
          But notice that since 2 and 3 are coprime, there are no integers that 
          will satisfy the equation $2^a = 3^b$, which contradicts our original 
          assumption that there exists a fraction, $\frac{a}{b}$ that satisfies
          $2^\frac{a}{b} = 3$. Thus, $\log_{2}3$ is irrational. \hfill $\blacksquare$
          \item Let $x = \sqrt2^{\sqrt2}$ and let $y = \sqrt2$. Then 
          \begin{align*}
            x^y = 2,
          \end{align*}
          Which is rational, hence, there exists two numbers $x,y$, such that 
          $x^y$ is rational. \hfill $\blacksquare$
          \item Dividing $x^2 -3y^2 = 2$ by 3 and taking the remainder gives 
          \begin{align*}
            x^2 = 2 + 3k,
          \end{align*}
          for some integer $k$. But notice that $x^2$ can only return a value 
          in the form $x^2 = 3m$ or $x^2 = 1 + 3n$ for some integers $m$ and $n$
          when divided by 3. Thus, the equation $x^2-3y^2 = 2$ has no integer 
          solutions.
\end{enumerate}
\end{document}